Manuscript_v0.5_genetic_covariances

### 2020-11-04 R/Analysis_manuscript_mash_GxE.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(bigsnpr)
#library(mashr)
#install_github("alice-macqueen/switchgrassGWAS")
library(switchgrassGWAS)
```

@@

Keep covariance matrices with point mass > 0.05 and add them to U_hyp

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(bigsnpr)
library(rlist)
#library(mashr)
#install_github("alice-macqueen/switchgrassGWAS")
library(switchgrassGWAS)
```

@@

Keep covariance matrices with point mass > 0.05 and add them to U_hyp.
Add them as single effects (the remaining phe are 0)
And add them as combinations if possible.

1. Make mash inputs for five & two phenotypes for eight sites. Standardize phenotypes and clump SNPs.
2. Find trait order.  The trait order is the same order as the 'phenotypes' vector.
3. Make U_hyp in trait order.
4. Run mash with U_hyp.
# ------- load for m_single to full mash part --
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
outputdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", "single_sites")
site_v <- list(TX1 = "TX1", TX2 = "TX2", TX3 = "TX3", OK = "OK", MO = "MO",
               NE = "NE", MI = "MI", SD = "SD")#, eight_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"), tx_sites = c("TX1", "TX2", "TX3"), north_sites = c("MO", "NE", "MI", "SD"))
subpop_v <- list(Gulf_and_Midwest = "363g_12.1M", Midwest = "134g_8.8M", Gulf = "229g_10.3M")
phe_mult <- list(flowering_5 = c("FL50", "dyln_fl50", "cgdd_12c_gr2fl", "crain_gr2fl",
               "crain_1d"), greenup_2 = c("GR50", "cgdd_12c_10d"))
inputfiles <- read_delim(file.path(workingdir, "analysis", "gwas",
                                   "inputkinship.txt"),  delim = " ", 
                                   col_names = "SNPfiles")
```
# make mashr inputs for 2 greenup and 5 flowering phenotypes via bigsnp2mashr
```{r}
j=2
k=3
for(j in seq_along(phe_mult)){
  for(k in c(1,3)){
phe_suffix <- paste(phe_mult[[j]], subpop_v[k], 
                    sep = "*.*")
snp <- snp_attach(inputfiles$SNPfiles[k])
gwas_rds <- c()
for(i in seq_along(phe_suffix)){
gwas_rds1 <- pvdiv_results_in_folder(path = file.path(outputdir), 
                                      pattern = paste0("GWAS_datatable*.*",
                                                       phe_suffix[i]))
gwas_rds <- c(gwas_rds, gwas_rds1)
}
phenotypes_1 <- str_sub(gwas_rds, start = 16, end = -42) %>%
    str_replace(., "_$", "")

phenotypes <- paste0(names(subpop_v)[k], "_", phenotypes_1)
numSNPs <- round(ceiling(1200000/length(phenotypes)^2)/1000)*1000
out1phe <- pvdiv_bigsnp2mashr(path = file.path(outputdir), 
                           snp = snp, gwas_rds = gwas_rds, 
                           phenotypes = phenotypes, numSNPs = numSNPs, 
                           clump = TRUE, scaled = TRUE, saveoutput = TRUE,
                           suffix = paste0(names(phe_mult)[j], "_phe_",
                                           names(subpop_v)[k], "_subpop"))
  }
}
```

# Now make U_hyp in trait order. Try programmatically. Tests here
```{r}
v <- matrix(data = 0, nrow=16, ncol=16)

i=2 # site
j=1 # phe
k=1 # subpop: G&M, M, Gulf
# test generate U_ed with point mass > 0.05 from one m_single run.
suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_mult[[j]][i])

m_single <- readRDS(file.path(outputdir, paste0("Strong_Effects1000SNPs_", 
                                                     suffix, ".rds")))

U_single <- m_single$fitted_g$Ulist[get_U_by_mass(m_single)]
names(m_single$fitted_g$Ulist)
U_s <- U_single[!names(U_single) %in% c("equal_effects", "identity", "simple_het_1", "simple_het_2", "simple_het_3")]

q=1
U_hyp <- list()

# test generate U_hyp for multiple phenotypes from one m_single run.
for(q in seq_along(names(U_s))){
    s_length <- dim(U_s[[1]])[1]
    hyp1 <- v
    hyp1[c((i*s_length-s_length+1):(i*s_length)),
         c((i*s_length-s_length+1):(i*s_length))] <- U_s[[q]]
    U_hyp <- list.append(U_hyp, hyp1)
}
```

# -------------------------
# Create U_hyp programmatically
```{r}
library(tidyverse)
library(cowplot)
library(bigsnpr)
library(rlist)
library(switchgrassGWAS)
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
outputdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", "single_sites")
site_v <- list(TX1 = "TX1", TX2 = "TX2", TX3 = "TX3", OK = "OK", MO = "MO",
               NE = "NE", MI = "MI", SD = "SD")#, eight_sites = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD"), tx_sites = c("TX1", "TX2", "TX3"), north_sites = c("MO", "NE", "MI", "SD"))
subpop_v <- list(Gulf_and_Midwest = "363g_12.1M", Midwest = "134g_8.8M", Gulf = "229g_10.3M")
phe_mult <- list(flowering_5 = c("FL50", "dyln_fl50", "cgdd_12c_gr2fl", "crain_gr2fl",
               "crain_1d"), greenup_2 = c("GR50", "cgdd_12c_10d"))
```

```{r}
j=1 # phe_mult: 1 is fl
i=1
k=1 # subpop 1 = Gulf   3 = G&M

U_single_list <- list()
# Make a list (from each phenotype) of lists of U_ed with point mass > 0.05.
for(i in seq_along(phe_mult[[j]])){
  suffix <- paste0("single_phe_", names(subpop_v)[k], "_", phe_mult[[j]][i])
  m_single <- readRDS(file.path(outputdir, paste0("Strong_Effects1000SNPs_", 
                                                  suffix, ".rds")))
  U_single1 <- m_single$fitted_g$Ulist[get_U_by_mass(m_single)]
  U_s1 <- U_single1[!names(U_single1) %in% c("equal_effects", "identity", "simple_het_1", "simple_het_2", "simple_het_3")]
  U_single_list <- list.append(U_single_list, U_s1)
}

# Using U_single_list, generate U_hyp for multiple phenotypes.

## part 1: determine size of matrix that U_ed will need to be
s_total <- 0

for(i in seq_along(U_single_list)){
    s_length <- dim(as.data.frame(U_single_list[[i]][1]))[1]
    s_total <- s_total+s_length 
  }

## part 2: Define null U_ed matrix
v <- matrix(data = 0, nrow=s_total, ncol=s_total) 
U_hyp <- list()
for(i in seq_along(U_single_list)){
  for(q in seq_along(names(U_single_list[[i]]))){
    s_length <- dim(as.data.frame(U_single_list[[i]][q]))[1]
    U_s1 <- matrix(unlist(U_single_list[[i]][q]), nrow = s_length, ncol = s_length)
    hyp1 <- v
    hyp1[c((i*s_length-s_length+1):(i*s_length)),c((i*s_length-s_length+1):(i*s_length))] <- U_s1
    U_hyp <- list.append(U_hyp, hyp1)
  }
}

# part 3: determine U_ed with the same names
all_names <- c()
for(i in seq_along(U_single_list)){
  all_names <- c(all_names, names(U_single_list[[i]]))
}
U_hyp_comb_df <- enframe(all_names) %>% group_by(value) %>% tally() %>% filter(n > 1)  # these U_ed names have two or more phenotypes with point mass > 0.05.

n=1
U_hyp_comb <- list()
for(n in seq_along(U_hyp_comb_df$value)){
  name_U <- U_hyp_comb_df$value[n]
  for(i in seq_along(U_single_list)){
    for(q in seq_along(names(U_single_list[[i]]))){
      if(i == 1 & q == 1){
        s_length <- dim(as.data.frame(U_single_list[[i]][q]))[1]
        hyp1 <- v
      }
      if(name_U == names(U_single_list[[i]])[q]){
        U_s1 <- matrix(unlist(U_single_list[[i]][q]), nrow = s_length, 
                       ncol = s_length)
        hyp1[c((i*s_length-s_length+1):(i*s_length)),c((i*s_length-s_length+1):(i*s_length))] <- U_s1
      }
    }
  }

  U_hyp_comb <- list.append(U_hyp_comb, hyp1)
}
# part 4: Combine U_single into a combined U_hyp if the names of the U_ed match. 
# Probably there are better ways to do this but this is the best I can think of, apart from doing every last possible combination. That will also suck because I don't have any way to generate covariances between phenotypes. So, eh. Most likely none of these will get used.

View(U_hyp_comb[[2]])
U_hyp <- c(U_hyp, U_hyp_comb)
```
So between the 'single phenotype' U_hyp and the combined U_hyp, that will give me 16 U_hyp for the five flowering phenotypes, and 8 U_hyp for the greenup phenotypes.

Got it! Now need to either save these U_hyp, or just use them in mash after I generate the relevant list.

# Run mash on multiple phenotypes using these U_hyp

j = 2; k = 1: greenup, Gulf

```{r}
j=2 # phe_mult 1 = flowering 2 = greenup
k=3 # subpop 1 = Gulf   3 = G&M

phe_suffix <- paste(phe_mult[[j]], subpop_v[k], 
                    sep = "*.*")
gwas_rds <- c()
for(i in seq_along(phe_suffix)){
gwas_rds1 <- pvdiv_results_in_folder(path = file.path(outputdir), 
                                      pattern = paste0("GWAS_datatable*.*",
                                                       phe_suffix[i]))
gwas_rds <- c(gwas_rds, gwas_rds1)
}
phenotypes_1 <- str_sub(gwas_rds, start = 16, end = -42) %>%
    str_replace(., "_$", "")

phenotypes <- paste0(names(subpop_v)[k], "_", phenotypes_1)
numSNPs <- round(ceiling(1200000/length(phenotypes)^2)/1000)*1000

m_out <- mash_standard_run(path = outputdir, numSNPs = numSNPs, 
                           U_hyp = U_hyp,
                           suffix = paste0(names(phe_mult)[j], "_phe_",
                                           names(subpop_v)[k], "_subpop"),
                           saveoutput = TRUE)
```

Another option, I suppose, is just running mash on multiple phenotypes for a very small subset of strong SNPs... just a thought. Would give covar between phenotypes, too, when now I just have covar within phenotypes. Really this is just using a much smaller subset of strong SNPs to define U_ed than I have been doing.

For whatever reason (unknown as of 2020-11-02), finding the data-driven covariance matrices has taken more than a whole weekend for flowering phenotypes (5) in the Gulf subpop. I fear errors/the worst but will let it run a while longer to see. In case it's the number of conditions, I tried to run a separate mash on greenup phenotypes (2) in the Gulf subpop. We'll see if that completes faster.

```{r}
(18+17+16+15+14+13+12+11+10+9+8+7+6+5+4+3+2+1)*3
10/513
```

### 2020-11-04 R/Manuscript_v0.5_genetic_covariances.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(asreml)
library(cowplot)
library(switchgrassGWAS)
```

@@

## bivariate analyses
```{r}
asr_1 <- asreml(cbind(PKLE, KBSM) ~ trait,
                random = ~us(trait, init = c(1,0.1,1)):vm(PLANT_ID, k_full), #+
                  #us(trait, init = c(1, 0.1, 1)):SUBPOP,
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1)), 
                #na.method(y = "omit", x = "omit"),
                data = fl50_cor_df, 
                workspace = "3gb")
asr_1 <- update.asreml(asr_1)
summary(asr_1)$varcomp

vpredict(asr_1, h2_PKLE ~ V1/(V1+V5))
vpredict(asr_1, h2_KBSM ~ V3/(V3+V7))
vpredict(asr_1, r_G ~ V2/((V1*V3)^0.5))
vpredict(asr_1, r_R ~ V6/((V5*V7)^0.5))

# now try adding a factor to split trait by subpopulation. 
# Nope. I don't think this is a good idea with the kinship matrix there too.
# Maybe try this later if I ever try and partition variance by individuals. Could do for subpops and for individuals/genotypes, also.
asr_2 <- asreml(cbind(PKLE, KBSM) ~ trait,
                random = ~us(trait, init = c(1,0.1,1)):vm(PLANT_ID, k_full) +
                  us(trait, init = c(1, 0.1, 1)):SUBPOP,
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1)), 
                #na.method(y = "omit", x = "omit"),
                data = fl50_cor_df, 
                workspace = "3gb")
asr_2 <- update.asreml(asr_2)
summary(asr_2)$varcomp
vpredict(asr_2, h2_PKLE ~ V4/(V1+V4+V8))
vpredict(asr_2, h2_KBSM ~ V3/(V3+V6+V10))
vpredict(asr_2, r_S ~ V2/((V1*V3)^0.5))
vpredict(asr_2, r_G ~ V5/((V4*V6)^0.5))

# below works way better (with fewer warnings) when initial values are given. Order for init argument is specified below this code box.
asr_3 <- asreml(cbind(PKLE, KBSM, CLMB) ~ trait,
                random = ~us(trait, init = c(1,0.1, 1, 0.1, 0.1, 1)):vm(PLANT_ID, k_full), 
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1)), 
                na.action = na.method(x = "omit"),
                data = fl50_cor_df, 
                workspace = "3gb")
asr_3 <- update.asreml(asr_3)
summary(asr_3)$varcomp

vpredict(asr_3, h2_PKLE ~ V1/(V1+V8)) # 93.80
vpredict(asr_3, h2_KBSM ~ V3/(V3+V10)) # 90.19
vpredict(asr_3, h2_CLMB ~ V6/(V6+V13)) # 70.58
vpredict(asr_3, r_PK ~ V2/((V1*V3)^0.5)) # 41.23
vpredict(asr_3, r_KC ~ V5/((V3*V6)^0.5)) # 76.57
vpredict(asr_3, r_CP ~ V4/((V1*V6)^0.5)) # 52.84
?na.method()
```
order for init: AA, BA, BB, CA, CB, CC
AA BA BB CA CB CC DA DB DC DD EA EB EC ED EE FA FB FC FD FE FF (6int) GG (7int) HH

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#library(asreml)
library(cowplot)
library(switchgrassGWAS)
```

@@

## bivariate analyses

asr_1: test bivariate analysis.
```{r}
asr_1 <- asreml(cbind(TX2, MI) ~ trait,
                random = ~us(trait, init = c(1,0.1,1)):vm(PLANT_ID, k_full), #+
                  #us(trait, init = c(1, 0.1, 1)):SUBPOP,
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1)), 
                #na.method(y = "omit", x = "omit"),
                data = fl50_cov_df, 
                workspace = "3gb")
asr_1 <- update.asreml(asr_1)
summary(asr_1)$varcomp

vpredict(asr_1, h2_TX2 ~ V1/(V1+V5))
vpredict(asr_1, h2_MO ~ V3/(V3+V7))
vpredict(asr_1, r_G ~ V2/((V1*V3)^0.5))
vpredict(asr_1, r_R ~ V6/((V5*V7)^0.5))

# now try adding a factor to split trait by subpopulation. 
# Nope. I don't think this is a good idea with the kinship matrix there too.
# Maybe try this later if I ever try and partition variance by individuals. Could do for subpops and for individuals/genotypes, also.
asr_2 <- asreml(cbind(PKLE, KBSM) ~ trait,
                random = ~us(trait, init = c(1,0.1,1)):vm(PLANT_ID, k_full) +
                  us(trait, init = c(1, 0.1, 1)):SUBPOP,
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1)), 
                #na.method(y = "omit", x = "omit"),
                data = fl50_cov_df, 
                workspace = "3gb")
asr_2 <- update.asreml(asr_2)
summary(asr_2)$varcomp
vpredict(asr_2, h2_TX2 ~ V4/(V1+V4+V8))
vpredict(asr_2, h2_MI ~ V3/(V3+V6+V10))
vpredict(asr_2, r_S ~ V2/((V1*V3)^0.5))
vpredict(asr_2, r_G ~ V5/((V4*V6)^0.5))
```

asr_3: trivariate analysis.  specifying initial values for variances and covariances.
```{r}
# below works way better (with fewer warnings) when initial values are given. Order for init argument is specified below this code box.
asr_3 <- asreml(cbind(TX2, MI, MO) ~ trait,
                random = ~us(trait, init = c(1,0.1, 1, 0.1, 0.1, 1)):vm(PLANT_ID, k_full), 
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1)), 
                na.action = na.method(x = "omit"),
                data = fl50_cov_df, 
                workspace = "3gb", maxiter = 30)
asr_3 <- update.asreml(asr_3)
summary(asr_3)$varcomp

vpredict(asr_3, h2_TX2 ~ V1/(V1+V8)) # 93.80
vpredict(asr_3, h2_MI ~ V3/(V3+V10)) # 90.19
vpredict(asr_3, h2_MO ~ V6/(V6+V13)) # 70.58
vpredict(asr_3, r_TX2MI ~ V2/((V1*V3)^0.5)) # 41.23
vpredict(asr_3, r_MIMO ~ V5/((V3*V6)^0.5)) # 76.57
vpredict(asr_3, r_TX2MO ~ V4/((V1*V6)^0.5)) # 52.84
?na.method()

asr_4 <- asreml(cbind(TX1, TX2, TX3, OK) ~ trait,
                random = ~us(trait, init = c(1, 0.1, 1, 0.1, 0.1, 1, 0.1, 0.1, 
                                             0.1, 1)):vm(PLANT_ID, k_full), 
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1, 0.1, 0.1, 
                                                     0.1, 0.1, 0.1, 0.1, 0.1)), 
                na.action = na.method(x = "omit"),
                data = fl50_cov_df, 
                workspace = "3gb", maxiter = 20)
asr_4 <- update.asreml(asr_4)
summary(asr_4)$varcomp

vpredict(asr_4, h2_TX1 ~ V1/(V1+V12)) # 93.80
vpredict(asr_4, h2_TX2 ~ V3/(V3+V14)) # 90.19
vpredict(asr_4, h2_TX3 ~ V6/(V6+V17)) # 70.58
vpredict(asr_4, h2_OK ~ V10/(V10+V21))
vpredict(asr_4, r_TX2MI ~ V2/((V1*V3)^0.5)) # 41.23
vpredict(asr_4, r_MIMO ~ V5/((V3*V6)^0.5)) # 76.57
vpredict(asr_4, r_TX2MO ~ V4/((V1*V6)^0.5)) # 52.84
```
order for init: AA, BA, BB, CA, CB, CC
AA BA BB CA CB CC DA DB DC DD EA EB EC ED EE FA FB FC FD FE FF (6int) GG (7int) HH

@@

# On server:
For both GR50 and FL50, in Gulf, Midwest, and G&M subpops.
-> subset fl50_cov_df and gr50_cov_df to these three individual subsets. Six subsets.
```{r}
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", 
                 Gulf_and_Midwest = c("Gulf", "Midwest"))
i=3
phe_df <- list(FL50 = fl50_cov_df, GR50 = gr50_cov_df)
j=2

cov_df_use <- phe_df[[j]] %>%
  filter(SUBPOP %in% subpop_v[[i]])
```

for Midwest, try just gardens with n>100 first.
```{r}
i=2
j=2
asr_3 <- asreml(cbind(TX2, MI, MO) ~ trait,
                random = ~us(trait, init = c(1,0.1, 1, 0.1, 0.1, 1)):vm(PLANT_ID, k_full), 
                residual = ~units:us(trait, init = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1)), 
                na.action = na.method(x = "omit"),
                data = cov_df_use, 
                workspace = "6gb", maxiter = 50)
asr_3 <- update.asreml(asr_3, maxiter = 100)
summary(asr_3)$varcomp

vpredict(asr_3, h2_TX2 ~ V1/(V1+V8)) # 93.80
vpredict(asr_3, h2_MI ~ V3/(V3+V10)) # 90.19
vpredict(asr_3, h2_MO ~ V6/(V6+V13)) # 70.58
vpredict(asr_3, r_TX2MI ~ V2/((V1*V3)^0.5)) # 41.23
vpredict(asr_3, r_MIMO ~ V5/((V3*V6)^0.5)) # 76.57
vpredict(asr_3, r_TX2MO ~ V4/((V1*V6)^0.5)) # 52.84
saveRDS(asr_3, "analysis/genetic-covariances/GR50_asreml_cov_model_3_gardens_Midwest_subpop.rds") 
# for the model running 2020-11-02 that will probably have a loglik around -778, which was run with i=2 and j=2.
```

```{r}

# try all eight gardens first.
asr_8 <- asreml(cbind(TX1, TX2, TX3, OK, MO, NE, MI, SD) ~ trait,
                random = ~us(trait, init = c(1, 0.1, 1, 0.1, 0.1, 1, 
                                             0.1, 0.1, 0.1, 1,
                                             0.1, 0.1, 0.1, 0.1, 1,
                                             0.1, 0.1, 0.1, 0.1, 0.1, 1,
                                             0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 1,
                                             0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 1)):vm(PLANT_ID, k_full), 
                residual = ~units:us(trait, init = rep(0.1, 36)), 
                na.action = na.method(x = "omit"),
                data = cov_df_use, 
                workspace = "6gb", maxiter = 240)
saveRDS(asr_8, "analysis/genetic-covariances/GR50_asreml_cov_model_8_gardens_Gulf_and_Midwest_subpop.rds") 
summary(asr_8)$varcomp
asr_8 <- update.asreml(asr_8)

summary(asr_8)$varcomp

saveRDS(asr_8, "analysis/genetic-covariances/GR50_asreml_cov_model_8_gardens_Gulf_and_Midwest_subpop.rds")

# for the model running 2020-11-03 that will probably have a loglik around ____, which was run with i=3 and j=2.

#saveRDS(asr_8, "analysis/genetic-covariances/FL50_asreml_cov_model_8_gardens_Gulf_subpop.rds") 
# for the model running 2020-11-02 that will probably have a loglik around -3978, which was run with i=1 and j=1.

8+7+6+5+4+3+2+1 # 36 var and covar in eight garden model.
# programmatically, each pair of two gardens, k and k+1. (special case of 8 & 1 also).
```
check model ran and saved ok on the server
```{r}
asr_8 <- readRDS("../analysis/genetic-covariances/GR50_asreml_cov_model_8_gardens_Gulf_subpop.rds")
summary(asr_8)$varcomp
vpredict(asr_8, h2_tx1 ~ V1/(V1+V38))
vpredict(asr_8, h2_tx2 ~ V3/(V3+V40))
vpredict(asr_8, h2_tx3 ~ V6/(V6+V43))
vpredict(asr_8, h2_ok ~ V10/(V10+V47))  # all sig > 0 minus 2SE, ok is the closest to zero... only 3.8%
vpredict(asr_8, h2_mo ~ V15/(V15+V52))
vpredict(asr_8, h2_ne ~ V21/(V21+V58))
vpredict(asr_8, h2_mi ~ V28/(V28+V65))
vpredict(asr_8, h2_sd ~ V36/(V36+V73))

vpredict(asr_8, cov_tx2tx1 ~ V2/((V1*V3)^0.5))  # sig pos

vpredict(asr_8, cov_tx3tx1 ~ V4/((V1*V6)^0.5))   # sig pos
vpredict(asr_8, cov_tx3tx2 ~ V5/((V6*V3)^0.5))   # sig pos

vpredict(asr_8, cov_oktx1 ~ V7/((V1*V10)^0.5)) 
vpredict(asr_8, cov_oktx2 ~ V8/((V3*V10)^0.5)) 
vpredict(asr_8, cov_oktx3 ~ V9/((V6*V10)^0.5))

vpredict(asr_8, cov_motx1 ~ V11/((V1*V15)^0.5)) 
vpredict(asr_8, cov_motx2 ~ V12/((V3*V15)^0.5))  # ** sig neg even plus 2SE
vpredict(asr_8, cov_motx3 ~ V13/((V6*V15)^0.5)) 
vpredict(asr_8, cov_mook ~ V14/((V10*V15)^0.5))

vpredict(asr_8, cov_netx1 ~ V16/((V1*V21)^0.5)) 
vpredict(asr_8, cov_netx2 ~ V17/((V3*V21)^0.5)) 
vpredict(asr_8, cov_netx3 ~ V18/((V6*V21)^0.5)) 
vpredict(asr_8, cov_neok ~ V19/((V10*V21)^0.5)) 
vpredict(asr_8, cov_nemo ~ V20/((V15*V21)^0.5))   # sig pos

vpredict(asr_8, cov_mitx1 ~ V22/((V1*V28)^0.5)) 
vpredict(asr_8, cov_mitx2 ~ V23/((V3*V28)^0.5)) # ** sig neg even plus 2SE
vpredict(asr_8, cov_mitx3 ~ V24/((V6*V28)^0.5)) 
vpredict(asr_8, cov_miok ~ V25/((V10*V28)^0.5)) 
vpredict(asr_8, cov_mimo ~ V26/((V15*V28)^0.5)) # sig pos
vpredict(asr_8, cov_mine ~ V27/((V21*V28)^0.5))

vpredict(asr_8, cov_sdtx1 ~ V29/((V1*V36)^0.5)) # ** sig neg even plus 2SE
vpredict(asr_8, cov_sdtx2 ~ V30/((V3*V36)^0.5)) # ** sig neg even plus 2SE
vpredict(asr_8, cov_sdtx3 ~ V31/((V6*V36)^0.5)) # ** sig neg even plus 2SE
vpredict(asr_8, cov_sdok ~ V32/((V10*V36)^0.5)) 
vpredict(asr_8, cov_sdmo ~ V33/((V15*V36)^0.5)) # sig pos
vpredict(asr_8, cov_sdne ~ V34/((V21*V36)^0.5)) 
vpredict(asr_8, cov_sdmi ~ V35/((V28*V36)^0.5))

#36.80566-(16.49249*2)
```
36.80566-(16.49249*2)

fit 7 (or more) bivariate models; compare h^2 estimates between them for A-H.
-> collect h^2 estimates and SE in tibbles, and compare/plot them.

----------------------
Fit trivariate models?
Try to fit 8-way model? Run these models on the server so my laptop isn't overloaded.
